LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-12-02 main.tex
Address reviewer #5, comment #1 and #2

\begin{abstract}
% FIXME Reviewer #5, comment #1: Abstract and introduction the objective and contribution of the paper are not clear; several points need to be clarified further.
% FIXME Reviewer #5, comment #2: For readers to quickly catch the contribution in this work, it would be better to highlight major difficulties and challenges, and original achievements to overcome them, in a clearer way in abstract and introduction.
We give an algorithmic introduction to Lagrangian coherent structures (LCSs) using a newly developed computational engine, LCS Tool. LCSs are most repelling, attracting and shearing material lines that form the centrepieces of observed tracer patterns in two-dimensional unsteady dynamical systems. LCS Tool implements the latest geodesic theory of LCSs for two-dimensional flows, uncovering key transport barriers in unsteady flow velocity data as explicit solutions of differential equations. After a review of the underlying theory, we explain the steps and numerical methods used by LCS Tool, and illustrate its capabilities on three unsteady fluid flow examples.
\end{abstract}

>>>>

\begin{abstract}
We give an algorithmic introduction to Lagrangian coherent structures (LCSs) using a newly developed computational engine, LCS Tool. LCSs are most repelling, attracting and shearing material lines that form the centrepieces of observed tracer patterns in two-dimensional unsteady dynamical systems. LCS Tool implements the latest geodesic theory of LCSs for two-dimensional flows, uncovering key transport barriers in unsteady flow velocity data as explicit solutions of differential equations. LCS Tool makes theoretical results accessible to the fluid mechanics community since implementing these results directly could be time consuming. After a review of the underlying theory, we explain the steps and numerical methods used by LCS Tool, and illustrate its capabilities on three unsteady fluid flow examples.
\end{abstract}
